### 2014-11-23 signature.tex
updates to signature page and bibliography
a few more updates to the signature page

\par This thesis is approved as a creditable and independent investigation by a candidate for the Master's of Science degree and is acceptable for meeting the thesis requirements for this degree.  Acceptance of this thesis does not imply that the conclusions reached by the candidate are necessarily the conclusions of the major department.

@@

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{230bp}\youradvisor\\
\hspace*{\fill}Thesis Advisor \hspace*{97bp}Date

@@

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{230bp}\departmenthead\\
\hspace*{\fill}Head, Math and Statistics \hspace*{40bp}Date

\end{document}

>>>>

\par This dissertation is approved as a creditable and independent investigation by a 
candidate for the Doctor of Philosophy degree and is acceptable for 
meeting the dissertation requirements for this degree. Acceptance of this does not imply 
that the conclusions reached by the candidates are necessarily the conclusions of the 
major department.

@@

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{194bp}\youradvisor\\
\hspace*{\fill}Dissertation Advisor \hspace*{47bp}Date

@@

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{194bp}\departmenthead\\
\hspace*{\fill}Head, Math and Statistics \hspace*{40bp}Date

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{194bp}Dean, Graduate School \hspace*{54bp}Date
\end{document}
